\documentclass[12pt]{homework}

\title{Student Information Form}
%\assignment{Homework, Week 1}
\duedate[]{}
\coursetitle{The City after Civil Rights}
\coursenumber{SOCY 368}
\author{Prof. Michael Bader}



%\printanswers
\begin{document}
\maketitle 
\noindent Please take some time to fill out the following information. This helps me get to know you better and what interests you. Use the front of the sheet to share things that you don't mind others knowing within the context of class. Please use the back to tell me anything that you might want me to know, even if it doesn't respond directly (or at all) to any of the questions. Thank you and I'm looking forward to a great semester!


\begin{questions}
\uplevel{\textbf{Personal Information}}
\question Please write your preferred name:

\question What year are you (circle one): Freshman\, Sophomore\, Junior\, Senior\, Other

\uplevel{\textbf{Class-Related Questions}}

\question In what cities have you lived? 
\begin{solution}[.5in]\end{solution}

\question Out of all of the classes that you could have taken at AU (or in the sociology major), why did you pick this one? 
\begin{solution}[.5in]\end{solution}

\question What do you know (or want to know) about the Civil Rights Movement?
\begin{solution}[.5in]\end{solution}

\uplevel{\textbf{Semester Goals \& Concerns}}
\question What are your goals for the semester (in this class and overall)? 
\begin{solution}[.5in]\end{solution}

\question What are your concerns about the semester (in this class and overall)?
\begin{solution}[.5in]\end{solution}

\question \textbf{ON THE BACK} please write at least one thing that you want me to know about you (I will not share these). Please also include responses or elaborations on anything above as well. 



\end{questions}

\end{document}